Digital Privacy and Cryptography

### 2014-12-04 LaTex/paper.tex
most updated

\documentclass[12pt]{article}
\usepackage{latexsym}

@@

@@

All business have the incentive to improve profit and without external incentives will strictly focus on profits. The two greatest external forces on corporations is government and public opinion. The government pressure on companies is non-existence and what force that is present is outdated. The public is less concerned about with drawbacks of the data privacy and more concerned with the benefits of the application. Most people ask what can it do for me instead of how does it work and what security measures are in place? These lack of incentive have lead to business tending to focus more what profit can be produced from personal data and not the long term impact it could have. There is a lack of research done by the companies producing these techonologies on the users. The negative side effects are not taken into consideration during the design process. Security is usually an after thought and privacy is never considered. This is evident in a recent study done by Cisco Canada in which they found "40 per cent of about 500 firms surveyed had security strategies" \cite{Blackwell}.

@@

\section{Ways to  Change}\label{sec:developers}
This section talks about the ways in which cryptography can help achieve digital privacy

@@

\clearpage
\begin{thebibliography}{99}
\bibitem{Albergotti}
	Albergotti, R. (2014, November 13). Facebook Gives Its Privacy Policy a Makeover. Retrieved November 16, 2014, {\sl http://blogs.wsj.com/digits/2014/11/13/facebook-gives-its-privacy-policy-a-makeover/}
\bibitem{Doctorow}
	Doctorow, C. (2014, November 12). Peak indifference-to-surveillance. Retrieved November 14, 2014, {\sl http://boingboing.net/2014/11/12/peak-indifference-to-surveilla-2.html}
\bibitem{Gomes}
	Gomes, L. (2014, October 20). Machine-Learning Maestro Michael Jordan on the Delusions of Big Data and Other Huge Engineering Efforts. Retrieved October 26, 2014, {\sl http://spectrum.ieee.org/robotics/artificial-intelligence/machinelearning-maestro-michael-jordan-on-the-delusions-of-big-data-and-other-huge-engineering-efforts}
\bibitem{Lawton}
	Lawton, V. (2013, May 23). New privacy challenges demand stronger protections for Canadians. Retrieved October 14, 2014
\bibitem{Lazer}
	Lazer, D., Kennedy, R., King, G., and Vespignan, A. (2014, March 14). The Parable of Google Flu: Traps in Big Data Analysis. Retrieved November 17, 2014.
\bibitem{Madden}
	Madden, M. (2014, November 12). Public Perceptions of Privacy and Security in the Post-Snowden Era. Retrieved November 15, 2014, {\sl http://www.pewinternet.org/2014/11/12/public-privacy-perceptions/}
\bibitem{Notley}
	Notley, T. (2014, August 4). Why digital privacy and security are important for development. Retrieved October 14, 2014, {\sl http://www.theguardian.com/global-development/poverty-matters/2011/aug/04/digital-technology-development-tool}
\bibitem{Nowak}
	Nowak, P. (2014, June 21). In era of revelation, privacy more important than ever. Retrieved October 14, 2014, {\sl http://business.financialpost.com/2012/06/21/in-era-of-revelation-privacy-more-important-than-ever}
\bibitem{Roughhol}
	Roughol, I. (2014, November 19). Uber's Privacy Scandal Is a Failure of Culture. Retrieved November 19, 2014, {\sl
	https://www.linkedin.com/today/post/article/ubers-privacy-scandal-failure-isabelle}
\bibitem{Schneier}
	Schneier, B. (2014, October 6). IPhone Encryption and the Return of the Crypto Wars. Retrieved November 23, 2014, {\sl https://www.schneier.com/blog/archives/2014/10/iphone \textunderscore encrypti \textunderscore 1.html}
\bibitem{Solove}
	Solove, D. (2014, November 12). People Care About Privacy Despite Their Behavior. Retrieved November 13, 2014, {\sl https://www.linkedin.com/today/post/article/20141112171953-2259773-people-care-about-privacy-despite-their-behavior}
\bibitem{WallBank}
	Wallbank,P. How much server space do Internet companies need to run their sites? {\sl http://paulwallbank.com/2012/08/23/how-much-server-space-do-internet-companies-need-to-run-their-sites/} (2012)

@@

\bibitem{Banayan}
	Banayan, A. (2014, November 4). 2 Ways Big Data Can Make You Happier. Retrieved November 5, 2014, from https://www.linkedin.com/pulse/article/20141104090919-80844253-2-ways-big-data-can-make-you-happier?trk=tod-home-art-list-large\textunderscore0
\end{thebibliography}

>>>>

\documentclass[12pt]{article}
\usepackage{latexsym}
\usepackage{setspace}
\doublespacing

@@

\clearpage

@@

All business have the incentive to improve profit and without external incentives will strictly focus on profits. The two greatest external forces on corporations is government and public opinion. The government pressure on companies is non-existence and what force that is present is outdated. The public is less concerned about with drawbacks of the data privacy and more concerned with the benefits of the application. Most people ask what can it do for me instead of how does it work and what security measures are in place? These lack of incentive have lead to business tending to focus more what profit can be produced from personal data and not the long term impact it could have. There is a lack of research done by the companies producing these techonologies on the users. The negative side effects are not taken into consideration during the design process. Security is usually an after thought and privacy is never considered. This is evident in a recent study done by Cisco Canada in which they found "40 per cent of about 500 firms surveyed had security strategies" \cite{Blackwell}. Just last week, Sony was hacked where a significant amount of employee information was leaked. Their are estimates of "100 terabytes of data" leaked containing information such as "list of employee salaries and bonuses; Social Security numbers and birth dates; HR employee performance reviews, criminal background checks and termination records" \cite{Zetter}.

@@

\section{Ways to  Change}\label{sec:developers}
It is clear that security and digital privacy need to be focused and strengthened. A developer needs to recognize this during the design of their system. They need to build into their system ways users can stay annonymous or delete private information when requested. Digital privacy should be the standard when creating web applications and a feature. What techonlogy can help developer keep personal information private?

There a wide range of Private Enhancing techniques using Crypotgraphy. This paper will focus on Private Digital Credentials, Type X remailers, and Onion Routing focusing on how these can allow of digital privacy.

\section{Private Digital Credentials}\label{sec:PDC}
What is it?
Digital Credentials are just information that can be used to qualify a certain propery. One Example would be a Laurier Digital Diploma whichs qualifies that a person graduated from Laurier University.  Private Digital Credentials are used as a way to qualify but keep anonymity for the presenter. The idea was first proposed by Daivd Chaum in 1985 \ref{Chaum}. He introduces the idea of unconditional untraceabile payments which used signatures called "blind signatures"\ref{Chaum}.

How does it work?
David Chaum uses the analogy of Private Digital Credentials to the use of a carbon-paper-lined envelope. Once the letter is inserted into the envelope any mark on the exterior of the envelope will be applied to the letter. A person could sign the letter without ever seeing the letter. The proposed system is one in which a person uses blind signatures to receive the banks authentication of a dollar and subtracts the amount from the account. The banks uses the same signatures for all transactions. The bank can verify any letter since it uses requires its transaction but cannot identify which envelope the letter came from. The ideas relies on the use of a zero knowledge proof. A zero knowledge proof uses a NP-Complete problem so a person can verify the solution in polynomial time but cannont solve in polynomial time. The idea of the letter inside envelope is the information you want proof without letting the person know what that information is.

How does it provide digital privacy?

\section{Type X Remailers}\label{sec:type-x}
What is it?

How does it work?

How does it provide digital privacy and its benefits?

\section{Onion Routing}\label{}
What is it?

How does it work?

How does it provide digital privacy and its benefits?

@@

\clearpage
\singlespace
\begin{thebibliography}{99}
\bibitem{Albergotti}
	Albergotti, R. (2014, November 13). Facebook Gives Its Privacy Policy a Makeover. Retrieved November 16, 2014, {\sl http://blogs.wsj.com/digits/2014/11/13/facebook-gives-its-privacy-policy-a-makeover/}
\bibitem{Doctorow}
	Doctorow, C. (2014, November 12). Peak indifference-to-surveillance. Retrieved November 14, 2014, {\sl http://boingboing.net/2014/11/12/peak-indifference-to-surveilla-2.html}
\bibitem{Gomes}
	Gomes, L. (2014, October 20). Machine-Learning Maestro Michael Jordan on the Delusions of Big Data and Other Huge Engineering Efforts. Retrieved October 26, 2014, {\sl http://spectrum.ieee.org/robotics/artificial-intelligence/machinelearning-maestro-michael-jordan-on-the-delusions-of-big-data-and-other-huge-engineering-efforts}
\bibitem{Lawton}
	Lawton, V. (2013, May 23). New privacy challenges demand stronger protections for Canadians. Retrieved October 14, 2014
\bibitem{Lazer}
	Lazer, D., Kennedy, R., King, G., and Vespignan, A. (2014, March 14). The Parable of Google Flu: Traps in Big Data Analysis. Retrieved November 17, 2014.
\bibitem{Madden}
	Madden, M. (2014, November 12). Public Perceptions of Privacy and Security in the Post-Snowden Era. Retrieved November 15, 2014, {\sl http://www.pewinternet.org/2014/11/12/public-privacy-perceptions/}
\bibitem{Notley}
	Notley, T. (2014, August 4). Why digital privacy and security are important for development. Retrieved October 14, 2014, {\sl http://www.theguardian.com/global-development/poverty-matters/2011/aug/04/digital-technology-development-tool}
\bibitem{Nowak}
	Nowak, P. (2014, June 21). In era of revelation, privacy more important than ever. Retrieved October 14, 2014, {\sl http://business.financialpost.com/2012/06/21/in-era-of-revelation-privacy-more-important-than-ever}
\bibitem{Roughhol}
	Roughol, I. (2014, November 19). Uber's Privacy Scandal Is a Failure of Culture. Retrieved November 19, 2014, {\sl
	https://www.linkedin.com/today/post/article/ubers-privacy-scandal-failure-isabelle}
\bibitem{Schneier}
	Schneier, B. (2014, October 6). IPhone Encryption and the Return of the Crypto Wars. Retrieved November 23, 2014, {\sl https://www.schneier.com/blog/archives/2014/10/iphone \textunderscore encrypti \textunderscore 1.html}
\bibitem{Solove}
	Solove, D. (2014, November 12). People Care About Privacy Despite Their Behavior. Retrieved November 13, 2014, {\sl https://www.linkedin.com/today/post/article/20141112171953-2259773-people-care-about-privacy-despite-their-behavior}
\bibitem{WallBank}
	Wallbank,P. How much server space do Internet companies need to run their sites? {\sl http://paulwallbank.com/2012/08/23/how-much-server-space-do-internet-companies-need-to-run-their-sites/} (2012)

@@

\bibitem{Banayan}
	Banayan, A. (2014, November 4). 2 Ways Big Data Can Make You Happier. Retrieved November 5, 2014, from https://www.linkedin.com/pulse/article/20141104090919-80844253-2-ways-big-data-can-make-you-happier?trk=tod-home-art-list-large\textunderscore0

\bibitem{Zetter}
	Zetter, K. (2014, December 3). Sony Got Hacked Hard: What We Know and Don’t Know So Far. Retrieved December 3, 2014, from http://www.wired.com/2014/12/sony-hack-what-we-know/

\bibitem{Goldberg}
	Goldberg, I., Wagner, D., and Brewer, E. (1997, January 21). Privacy-enhancing technologies for the Internet. Retrieved December 3, 2014, from http://www.cypherpunks.ca/~iang/pubs/privacy-compcon97.pdf

\bibitem{GoldbergTwo}
	Goldberg, I. (2007, December 1). Privacy Enhancing Technologies for the Internet III: Ten Years Later. Retrieved December 3, 2014, from http://www.cypherpunks.ca/~iang/pubs/pet3.pdf

\bibitem{Chaum}
	Chaum, D. (1985, October 10). Security without identification: Transaction systems to make big brother obsolete. Communications of the ACM, 1030-1044.
\end{thebibliography}
